Relevance-based Quantization of Scattering Features for Unsupervised Mining of Environmental Audio

### 2018-06-29 paper/revision/responseToReviewers.tex

As a preamble, we would like to thank the reviewers for their comments and suggestions. Following these comments, we made several changes to the article, which are summarized here. The next sections list our answers to each of the reviewer’s comments, with references to the revised manuscript (page, column, and paragraph) where appropriate.

\section{Answer to Reviewer 1}

\begin{enumerate}

\item \emph{I suggest that they only refer to ecoacoustics in the discussion by mentionning that this could be tested on other audio scenes as those recorded in natural environments.}

$\rightarrow$ The abstract introduction, background section and conclusion have been rewritten to widen the scope of application of the proposed method and suggest the ecoacoustic as potential area of interest for further research.

@@

\item \emph{The dataset is too quickly described. I had to read ref\#36 to understand how it was built and made of. It would be nice to have an example of a labelled recording either as a spectrogram or scalogram to estimate the complexity of the scenes recorded. The event classes should also be detailed.}

$\rightarrow$ VL

\item \emph{It is a pity that the methods are not directly compared with the different strategies reported in ref\#36.}

$\rightarrow$
Since the tasks are different, it is not straightforward to compare the proposed methods with the approaches of ref\#36. In the former, we propose a method for acoustic scene similarity retrieval, while the latter discusses the problem of scene classification. In similarity retrieval, we would like to find other recordings in the dataset that are as similar to the original as possible (which here is defined as being in the same class). In scene classification, the task is to assign a class to each recording. In this sense, similarity retrieval is a more general problem. For our experiments, we calculate the p@k curves for each proposed method, allowing us to analyze the distribution of recordings most similar to a particular query recording. The classification setting is reproduced for $k = 1$, with the p@1 measure corresponding to the leave-one-out classification accuracy of nearest neighbors. As such, the classification task is a special case of the similarity retrieval setting considered here. We have modified the manuscript to make this distinction more clear.

It is also worth considering that the BOF model is used differently in scene retrieval (our use case) and scene classification (ref\#36). In scene retrieval, given two scenes (a and b) modeled using GMMs (A and B), the similarity between two scenes is the similarity between A and B. In scene classification, each class of sound scenes (park, boulevard) are modeled using a GMM (P, B). Then, for an unknown scene $u$, the likelihood of $u$ given P and B are computed. The scene $u$ is then labeled P if the likelihood of $u$ given P is greater than the likelihood of $u$ given B.

Even if the technical aspects are quite close, the way the algorithm is designed is different as the tasks they have to solve are differents. A synthetic description of the matter is added to Section 2.

@@

\section{Answer to Reviewer 2}

\begin{enumerate}

\item \emph{Only two applications are considered in the literature review, bioacoustics and urban sound environment, but they allow to present a problem that also exists in other application areas.}

$\rightarrow$ We reformulated in a more abstract way the task we attempt to solve, and give potential areas of applications in the introduction and conlusion sections.

@@

$\rightarrow$
As discussed above in the response to the first reviewer, the application in the DCASE 2013 paper, classification, is different from the one proposed in our work, similarity retrieval. For classification, the BOF approach is indeed not the state of the art. However, in acoustic scene similarity retrieval, we are not aware of any systems which outperform the BOF. As such, it is indeed the state of the art for the similarity retrieval task. The manuscript has been revised to clarify this point.

\item \emph{It would be interesting to see the contribution to the results of the Gammatone wavelet in comparison to Morlet or another more classical wavelet.}

$\rightarrow$ VL

\item \emph{There are several parameters that must be set in the experimentation. The reader may want to know if there is any specific parameter that is critical.}

$\rightarrow$ Considering the features design, we set the parameters to widely used values that have shown to be robust. We also ran a sensitivity analysis for the parameters that controls the proposed algorithm: scaling parameter $q$ and the number of clusters $M$. None of them are found to be critical providing that they are set in a reasonable range. It is worth noting that the scaling method is specifically designed for reducing sensitivity compared to the direct RBF kernel formulation.

\item \emph{What about M?}

$\rightarrow$ A discussion about the setting of the parameter M is added at the end of Section 6.3.
